### 2018-08-07 paper/design.tex
clarifying adversary effect statement in design overview

\sonja{will frame and structure (A) squad overlay (prediction) (B)
  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
  if not included earlier (F) out-of-band}
\commentDaniel{I suggest the following structure:
  (A) \Sphinxes
  (B) SPOR (global overlay)
  (C) SPORES (local overlay).
  My original idea was to make \Sphinxes its own section before the design 
  section instead of a subsection in the design section.}

@@

Figure~\ref{fig:outline} shows the components needed to obtain the
routing information for the headers.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline_figure_only.pdf_tex}
  \caption{\label{fig:outline}%
    %\commentDaniel{We must adapt this figure to the text.}%
    Outline of \name's components. Users' squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them with random peers (\cref{ssec:device_availability}); using the two 
    overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
    These protocols enable secure file transfer between users 
    (\cref{ssec:por}).}
\end{figure}

@@

\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  according to Figure~\ref{fig:outline}, and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.
\item[Onion Routing.] Put simply, in onion routing, the sender creates
  a source route and 
  encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on
  Sphinx~\cite{Sphinx}, with some modification to allow for the
  changes above, described in \cref{Sphinxes}.
\end{description}

\subsection{Taxonomy of anonymous communication protocols}

To present the different parts of \name in details, 
we align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They characterize anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure.]
    It describes the characteristics of the network nodes, the connections between 
    them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization);
    \end{enumerate*}

@@

Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
source-bounded random walk (communication 
model),
\Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active \sonja{global?} adversary can learn the 
entire set).

>>>>

% \sonja{will frame and structure (A) squad overlay (prediction) (B)
%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
%   if not included earlier (F) out-of-band}
% \commentDaniel{I suggest the following structure:
%   (A) \Sphinxes
%   (B) SPOR (global overlay)
%   (C) SPORES (local overlay).
%   My original idea was to make \Sphinxes its own section before the design 
%   section instead of a subsection in the design section.}

@@

% Figure~\ref{fig:outline} shows the components needed to obtain the
% routing information for the headers.

% \begin{figure}[t]
%   \centering
%   \def\svgwidth{0.8\columnwidth}
%   \import{figures/}{outline_figure_only.pdf_tex}
%   \caption{\label{fig:outline}%
%     %\commentDaniel{We must adapt this figure to the text.}%
%     Outline of \name's components. Users' squads of devices are circled in gray. 
%     From top to bottom: a user's devices collaborate through the Squad Overlay 
%     (\cref{sec:squad_overlay}); online devices globally share information about 
%     them with random peers (\cref{ssec:device_availability}); using the two 
%     overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
%     These protocols enable secure file transfer between users 
%     (\cref{ssec:por}).}
% \end{figure}

@@

\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  by an overlay and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way,
  resulting in a source-bounded random walk.
\item[Onion Routing.] Put simply, in onion routing, the sender creates
  a source route and 
  encapsulates the payload and next-hop information in layers (by
  encryption), that are \emph{peeled} (decrypted) one by one along the
  route. By virtue of these layers, the forwarding nodes on the
  route do not know where on the route they are and thus whether they
  have received a packet directly from the sender or some other
  intermediate node. We base our format for layering and peeling on
  Sphinx~\cite{Sphinx}, with some modification to allow for the
  changes above, described in \cref{Sphinxes}.
\end{description}

%\subsection{Taxonomy of anonymous communication protocols}

To present the different parts of \name in detail, 
we align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols} .
They characterize anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure.]
    It describes the characteristics of the network nodes, the connections between 
    them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization);
    \end{enumerate*}

@@

Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
\Sphinxes provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is hybrid source-hop-by-hop routed, a
source-bounded random walk (communication 
model),
\Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).
